Identifying Drawings with the Quick Draw Challenge

### 2018-12-01 report/report_draft.tex
add report pdf

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Identifying Drawings with the Quick Draw Challenge},
            pdfauthor={Blue Team},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Identifying Drawings with the Quick Draw Challenge}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Blue Team}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

@@

\hypertarget{theory-literature-review}{%
\section{Theory \& Literature Review}\label{theory-literature-review}}

CNN with dilation is preferable to LSTM because it's presumably faster.
We can cite some papers here.

\hypertarget{hypotheses}{%
\section{Hypotheses}\label{hypotheses}}

@@

\(H_a:\) Prediction will go up when we use regularization

\hypertarget{data}{%
\section{Data}\label{data}}

We got our data from Google/Kaggle

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-QuickDra10}{}%
Google. 2018. ``Quick, Draw! Doodle Recognition Challenge \textbar{}
Kaggle.'' \url{https://www.kaggle.com/c/quickdraw-doodle-recognition}.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Identifying Drawings with the Quick Draw Challenge},
            pdfauthor={Group 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Identifying Drawings with the Quick Draw Challenge}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Group 3}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

@@

\section{Introduction}\label{introduction}

Our team has based our project idea on the ``Quick, Draw!'' Kaggle
competition which classifies user drawings into one of 345 label
categories. Many drawings were incomplete or failed to match the label.
The challenge was to effectively build a recognizer that could work with
this noisy data. The challenge was unique from an algorithmic
perspective because the data included both temporal and spatial
components; areas that have traditionally used two different types of
Neural Network Architectures. Our team attempted to provide a solution
using a subset of the data, to the Kaggle problem, while taking a more
in depth look at potential pitfalls and modeling strategy, without
having to use extensive computational resources.

\section{Methods}\label{methods}

First, we got our data from Google/Kaggle. CNNs are traditionally known
to work well with spatial data, which prompted us to process the
original csv files to images of the drawings.

@@

\(H_a:\) Prediction will go up when we use regularization.

\(H_a:\) Run neural networks without any activations.

\(H_a:\) Try different architectures- number of layers, different (or
no) activations

\(H_a:\) CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

\section{Results}\label{results}

@@

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

\section{Appendix}\label{appendix}

Add computer code, plots, and other relevant technical details that will
help me evaluating your work.

\section*{Statement of contribution}\label{statement-of-contribution}
\addcontentsline{toc}{section}{Statement of contribution}

\hypertarget{refs}{}
\hypertarget{ref-QuickDra10}{}
Google. 2018. ``Quick, Draw! Doodle Recognition Challenge \textbar{}
Kaggle.'' \url{https://www.kaggle.com/c/quickdraw-doodle-recognition}.
